---
title: "Intro to dplyr -  Lab"
author: "My Tran"
output: html_document
---
```{r}
library(tidyverse)
```

In the package `dplyr` there is a dataset called `starwars`. 

```{r}
glimpse(starwars)
```


We're going to use this to practice some data wrangling with `dplyr`. 

First, we filter by species to only see the humans, and use that subset to plot a scatter plot of their height and mass.  

```{r}
humans <- starwars %>% filter(species == "Human")
plot(humans$height, humans$mass)

starwars %>% filter(species == "Human") %>% plot(mass ~ height, data = .)

```

Now, change this to see the same plot for the Droids. 

```{r}
humans <- starwars %>% filter(species == "Droid")
plot(humans$height, humans$mass)

starwars %>% filter(species == "Droid") %>% plot(mass ~ height, data = .)

```


How many characters are from each planet?

```{r}
starwars %>% group_by(homeworld) %>% summarise(n())


```

If you wanted to arrange this in descending order, what would you add to the pipe? 

```{r}
starwars %>% group_by(homeworld) %>% summarise(n=n()) %>% arrange(desc(n))

```

Find the average height for each eye color.

```{r}
starwars %>% group_by(eye_color) %>% summarise(mean(height))

```

What's with the NAs? Filter down to just brown eyes find out. 


```{r}
starwars %>% group_by(eye_color) %>% summarise(mean(height)) %>% filter(eye_color == "brown")

```

Okay, so we have missing data here. Try summarising with `na.omit(height)` instead of just `height` or adding `na.rm = T` to the mean function inside summarize. 


```{r}
starwars %>% group_by(eye_color) %>% summarise(mean(na.omit(height))) %>% filter(eye_color == "brown")

```

So, who is the tallest male? 

```{r}
starwars %>% filter(sex == "male" & height == max(na.omit(height)))
filter(starwars, sex == "male", height == max(na.omit(height)))
```

How many blue eyed women are there? 

```{r}
starwars %>% filter(sex == "female" & eye_color == "blue") %>% summarise(blue_eyed_women = n())
```

How many genders are there? 

```{r}
starwars<- na.omit(starwars) 
starwars %>%  group_by(gender) %>% summarise(number_genders = nrow(gender))

```
